EDA of DSRCT Samples

### 2024-10-29 analyses/cell-type-dsrct/exploratory_analysis/01-marker-gene-tumor-classification.Rmd

# The current data directory, found within the repository base directory
data_dir <- file.path(repository_base, "data", "2024-07-08")
#sample_dir <- file.path(data_dir, "SCPCP000013", params$sample_id)

@@

  #save plots
  ggsave(
    filename = paste0(
      '../plots/marker_expression_',
      names(umap_df_list)[i],
      '.png'
    ),
    plot = p,
    width = 6,
    height = 6,
    units = 'in',
    dpi = 150
  )
}

@@

  #save plots
  ggsave(
    filename = paste0(
      '../plots/marker_distribution_',
      names(umap_df_list)[i],
      '.png'
    ),
    plot = p,
    width = 6,
    height = 6,
    units = 'in',
    dpi = 150
  )
}
```

@@

  #save plots
  ggsave(
    filename = paste0(
      '../plots/marker_distribution_zscaled_',
      names(umap_df_list)[i],
      '.png'
    ),
    plot = p,
    width = 6,
    height = 6,
    units = 'in',
    dpi = 150
  )

@@

We could either count any cell that expresses at least one marker gene > 0 as a tumor cell, or look at the combined expression. 
Let's start with classifying tumor cells as tumor if any marker gene is present (z-score > 0). 
This also means the sum of all z-scores > 0.

@@

  #save plots
  ggsave(
    filename = paste0(
      module_base,
      '../plots/UMAP_classification_cluster_',
      names(umap_df_list)[i],
      '.png'
    ),
    plot = p,
    width = 6,
    height = 6,
    units = 'in',
    dpi = 150
  )

@@

## Save outputs 
```{r}
# get an RDS of the processed data
saveRDS(sce_file_list, '../results/SCPCP000013_sce_file_list.rds')
```

>>>>

# The current data directory, found within the repository base directory
data_dir <- file.path(repository_base, "data", "current")
#sample_dir <- file.path(data_dir, "SCPCP000013", params$sample_id)

@@

  #save plots
  ggsave(
    filename = paste0(
      module_base,
      '/plots/marker_expression_',
      names(umap_df_list)[i],
      '.png'
    ),
    plot = p,
    width = 6,
    height = 6,
    units = 'in',
    dpi = 150
  )
}

@@

  #save plots
  ggsave(
    filename = paste0(
      module_base,
      '/plots/marker_distribution_',
      names(umap_df_list)[i],
      '.png'
    ),
    plot = p,
    width = 6,
    height = 6,
    units = 'in',
    dpi = 150
  )
}
```

@@

  #save plots
  ggsave(
    filename = paste0(
      module_base,
      '/plots/marker_distribution_zscaled_',
      names(umap_df_list)[i],
      '.png'
    ),
    plot = p,
    width = 6,
    height = 6,
    units = 'in',
    dpi = 150
  )

@@

We could either count any cell that expresses at least one marker gene > 0 as a tumor cell, or look at the combined expression. 
Let's start with classifying tumor cells as tumor if any marker gene is present (z-score > 0).

@@

  #save plots
  ggsave(
    filename = paste0(
      module_base,
      '/plots/UMAP_classification_cluster_',
      names(umap_df_list)[i],
      '.png'
    ),
    plot = p,
    width = 6,
    height = 6,
    units = 'in',
    dpi = 150
  )

@@

## Save outputs 
```{r}
# get an RDS of the processed data
saveRDS(sce_file_list, '../results/SCPCP000013_sce_file_list.rds')
# get an RDS of the UMAP data with marker genes
saveRDS(umap_df_list, file.path(module_base, 'results/SCPCP000013_umap_df_list.rds'))
```
